Notes

### 2020-04-02 Notes/Notes.tex
small update to Notes

Another systematic error is introduced when allowing different qubit-wise anneal schedules $A(s) \to A_i(s)$ and $B(s) \to B_i(s)$.
If $B_i(0) \neq B_j(0)$ for $i \neq j$ the initial Hamiltonian, and if $B_i(1) \neq B_j(1)$ for $i \neq j$ the final Hamiltonian is effectively different from what was implemented.
Therefore shifted anneal schedules on DWave cannot be set too large.
It in principle possible to extend the anneal schedule beyond the range $s \in [s_I, s_F]$ with $s_I < 0$ and $s_F > 1$ such that, depending on how the $B_i$ are extrapolated, $B_i(s_I) = B_j(s_I)$ and $B_i(s_F) = B_j(s_F)$ for $i \neq j$ and equivalently for the $A_i$.
We also allow our simulations to incorporate different qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
Additionally, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.

@@

A quick study below. We run a simulation with anneal offsets similar to what we ran on DWave (Fig.~\ref{dwave_result}). We see that if we apply a delay on qubits with small values and advance qubits with of $h_i$ (binary), then the performance improves. And vice versa. This is completely unexpected from the point of view of many-body localization. Because this result was so surprising, we wrote this simulator. Under DWave conditions (embedded problem, non-linear anneal schedule, truncating offset), we are able to reproduce this behavior (fig~\ref{fig:proba_dwave}). Here I note that if we run the idealized scenario (more importantly, without embedding), the behavior is reverse, and is consistent with what is expected due to many-body localization.

>>>>

Another systematic error is introduced when allowing different qubit-wise anneal schedules $A(s) \to A_i(s)$ and $B(s) \to B_i(s)$.
If $B_i(0) \neq B_j(0)$ for $i \neq j$ the initial Hamiltonian, and if $B_i(1) \neq B_j(1)$ for $i \neq j$ the final Hamiltonian is effectively different from what was implemented.
Therefore shifted anneal schedules on DWave cannot be set too large. We also allow our simulations to incorporate different qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
It in principle possible to extend the anneal schedule beyond the range $s \in [s_I, s_F]$ with $s_I < 0$ and $s_F > 1$ such that, depending on how the $B_i$ are extrapolated, $B_i(s_I) = B_j(s_I)$ and $B_i(s_F) = B_j(s_F)$ for $i \neq j$ and equivalently for the $A_i$.
Therefore, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.

@@

A quick study below. We run a simulation with anneal offsets similar to what we ran on DWave (Fig.~\ref{fig:dwave_result}). We see that if we apply a delay on qubits with small values and advance qubits with of $h_i$ (binary), then the performance improves. And vice versa. This is completely unexpected from the point of view of many-body localization. Because this result was so surprising, we wrote this simulator. Under DWave conditions (embedded problem, non-linear anneal schedule, truncating offset), we are able to reproduce this behavior (fig~\ref{fig:proba_dwave}). Here I note that if we run the idealized scenario (more importantly, without embedding), the behavior is reverse, and is consistent with what is expected due to many-body localization.
